### 2017-07-20 01-intro.tex
Polish newness for journal, author bios. Make system descr a subsubsection

A bird's-eye view of the work in this paper, without any technical detail, has been
published at CCGrid-2016~\cite{10.1109/CCGrid.2016.98}. The technical descriptions
in Section~\ref{sec-gpu-design} and evaluation of our accelerator contributions in
Section~\ref{sec-gpu-evaluation} and Figures \ref{gpu-sweep}, \ref{gpus-fig}
and~\ref{gpus-v-sweep} have not been published before.
The results of our distributed contribution
have been previously published at the 2016 ParLearning
workshop~\cite{DBLP:conf/ipps/El-HelwHLAWB16}, where it earned a best-paper
award. In summary, nearly half of the work in this paper consists of new, unpublished
material.

>>>>

A bird's-eye view of the work in this paper, without any technical detail, has been
published at CCGrid-2016~\cite{10.1109/CCGrid.2016.98}. The technical
description and evaluation of our contributions
in Sections \ref{sec-design-sequential} and~\ref{sec-gpu},
Table~\ref{table-python-comparison}
and Figures \ref{gpu-sweep}, \ref{gpus-fig}
and~\ref{gpus-v-sweep} have not been published before.
The results of our distributed contribution
have been previously published at the 2016 ParLearning
workshop~\cite{DBLP:conf/ipps/El-HelwHLAWB16}, where it earned a best-paper
award. In summary, about 40\% of the work in this paper consists of new, unpublished
material.
